HUME: Human UCCA-Based Evaluation of Machine Translation

### 2016-03-16 paper/main.tex

HUME operates by aggregating human assessments of the translation quality of individual
semantic units in the source sentence.
Importantly, HUME only requires semantically annotating the source sentence,
thus avoiding the annotatation of machine-generated text 
and allowing re-use of the source semantic annotation for measuring the quality
of different translations of the same source sentence.
By basing the measure on a direct comparison
of the source and translation we avoid the difficulties engendered by using
reference translations, albeit at the cost of imposing the additional requirement
that the evaluator be proficient in both the source and target languages.
See \secref{sec:hmeant_comp}.

@@

@@

\subsection{Monolingual vs. Bilingual Evaluation}
+/- expects to cover the whole hypothesis with annotations, whereas HMEANT 'gives up' when the
hypothesis is not intelligible, giving a zero score to the bad frame/whole sentence.
This can be a good decision for HMEANT, since our way may artificially boost the chances of
understanding the sentence.

@@

\subsection{XXX to be moved}

HMEANT shares much of HUME's motivation for providing a
measure that decomposes over semantic units, rather than strings. On the other
hand, HMEANT focuses on verbal
argument structures, ignoring other pervasive phenomena such as nominal predicates, inter-clause
relations and copula clauses.
HUME further diverges from both HMEANT (as well as the shallow automatic BLEU and
METEOR measures) in not requiring a reference.
Instead, it compares the source directly with the output
translation. We see this difference as crucial where semantic analysis is concerned, as it
is often impossible to assign a semantic structure to a low quality MT output sentence.

%See \secref{sec:hmeant_comp} for a more elaborate discussion of the differences
%between HUME
%and HMEANT.
% This is here!

For instance, consider the sentence ``A coronary angioplasty may not be technically possible'',
which was translated by one of the systems we experimented with as
``Eine koronare Angioplastie kann nicht technisch m{\"o}glich'', i.e., the main verb ``sein'' (``be'') is omitted.
While this may be interpreted is a minor error, HMEANT will assign it a very low score, as it failed to
translate the main verb. We understand that this is a design feature of HMEANT:
if the translation per se cannot be annotated with verbal argument structure
(for whatever reason, including incomprehensibility), it cannot convey the meaning.
HMEANT thus makes a stricter check of whether the translation can be understood
than we do.

Several experiments with HMEANT applied to languages other than English
\parcite{bojar:wu:ssst:2012,birch-EtAl:2013:WMT,chuchunkov-tarelkin-galinskaya:2014:SSST-8}
indicated that HMEANT does not address some important phenomena.
We conducted an analysis of the English UCCA Wikipedia
corpus, comprising
of 5324 sentences,
in order to assess their frequency: \begin{inparadesc}
\item[Copula clauses] are treated in HMEANT simply as instances of the main verb ``be'', which
generally does not convey the meaning of these clauses. They appear in 21.7\% of the sentences,
according to a conservative estimates that only considers non-auxilliary instances of ``be''.
\item[Nominative argument structures,] which are completely ignored under HMEANT are in fact highly
pervasive, appearing in 48.7\% of the sentences.
\item[Linkers] expressing an inter-relation between
clauses (mainly discourse markers and coordinating conjunctions) appear in 56\% of the
sentences\footnote{Argument structures and linkers are explicitly marked in UCCA. We identified
  non-auxilliary instances of ``be'' and nouns using the NLTK standard tagger.}.
\end{inparadesc}

\subsection{from e-mails}

UCCA-Eval in contrast to HMEANT:

- needs *very* trained UCCA annotators
- we were not very quick at explaining even the Eval annotations, but I guess we could have done better
+ relies only on one structure
+ relies on automatic alignment (in the form of hints only)
These two positive design decisions are in line with what Dekai observed for HMEANT
(see the abstract of http://repository.ust.hk/ir/Record/1783.1-66107): IAA of SRL drops from 90
to 61 when the two aligned structures are from two different annotators.

Actually, I think this is a +/- . UCCA-Eval only needs the semantic evaluation done once for a given test source, whereas for the HMEANT set-up you have to keep annotating MT output. That's a + for UCCA-Eval. However we need bilingual annotators, which should be a -. Of course we could align translation and reference using monolingual annotators, but then we have the problem of alignment.
In the *MEANT papers they mainly test by either
A) correlating the metric to ranking judgements; or
B) using automated versions of the metric for tuning MT systems

@@

Differences of our approach:

The annotation experiment that we just conducted differs in two main ways from HMEANT:
1) The semantic framework is different - UCCA vs SRL - and SRL has problems which Omri lists below, some of which Dekai dismissed when they were brought up. Maybe these problems do not matter for MT evaluation or tuning, but I think this would have to be determined empirically.
2) The annotation process is different. We semantically annotate the source, then automatically project it to the translation, and ask bilingual annotators to assess whether this projection shows a good or bad translation. In HMEANT they semantically annotate both the reference and the translation, then align these manually, and assess to what extent they match.

Advatages of our approach:
Here is an additional argument to support the need for target-only intelligibility:
http://www.aclweb.org/anthology/W14-4005
see Table  3 and the text in Section 5.2.
The more frames can people annotate in the hypothesis, the better the hypothesis overall.

>>>>

HUME operates by aggregating human assessments of the translation quality of individual
semantic units in the source sentence.
Importantly, HUME only requires semantically annotating the source sentence,
thus avoiding the annotation of machine-generated text 
and allowing re-use of the source semantic annotation for measuring the quality
of different translations of the same source sentence.
By basing the measure on a direct comparison
of the source and translation we avoid the difficulties engendered by using
reference translations, albeit at the cost of imposing the additional requirement
that the evaluator be proficient in both the source and target languages.
See \secref{sec:hmeant_comp}.

@@

HMEANT shares much of HUME's motivation for providing a
measure that decomposes over semantic units, rather than strings. On the other
hand, there are important differences in design decisions, which we summarize in this
section.

First of all, the annotation process is different. We semantically annotate the
source, then automatically project it to the translation, and ask bilingual
annotators to assess whether this projection shows a good or bad translation. In
HMEANT, they semantically annotate both the reference and the translation, then
align these manually, and assess to what extent they match.

HMEANT focuses on verbal
argument structures, ignoring other pervasive phenomena such as nominal predicates, inter-clause
relations and copula clauses. Some of the uncovered cases were already observed
in previous applications of HMEANT to languages other than English (see \perscite{birch-EtAl:2013:WMT} for German, \perscite{bojar:wu:ssst:2012} for
Czech and by \perscite{chuchunkov-tarelkin-galinskaya:2014:SSST-8} for Russian)
but the problems are apparent in English as well.

We conducted an analysis of the English UCCA Wikipedia
corpus, comprising
of 5324 sentences,
in order to assess their frequency: \begin{inparadesc}
\item[Copula clauses] are treated in HMEANT simply as instances of the main verb ``be'', which
generally does not convey the meaning of these clauses. They appear in 21.7\% of the sentences,
according to a conservative estimates that only considers non-auxilliary instances of ``be''.
\item[Nominative argument structures,] which are completely ignored under HMEANT are in fact highly
pervasive, appearing in 48.7\% of the sentences.
\item[Linkers] expressing an inter-relation between
clauses (mainly discourse markers and coordinating conjunctions) appear in 56\% of the
sentences\footnote{Argument structures and linkers are explicitly marked in UCCA. We identified
  non-auxilliary instances of ``be'' and nouns using the NLTK standard tagger.}.
\end{inparadesc}

\subsection{Cost of Structural Annotation}

HMEANT structural annotation (semantic role labelling, SRL), similar to e.g.
PropBank
\parcite{palmer2010semantic}, is designed to be very simple and easy to explain
to lay annotators.
HUME relies on UCCA, which is arguably more abstract, harder to
explain, and thus more expensive to obtain.

On the other hand, HUME 
needs the semantic annotation
done once for a given source sentence, whereas for the HMEANT set-up, every new
MT output has to be structurally annotated.

@@

HUME uses just one structural annotation (for the source) while HMEANT relies on
two independently constructed structural annotations (for both the reference and
the candidate translation).

We see this difference as crucial where semantic analysis is concerned, as it
is often impossible to assign a semantic structure to a low quality MT output sentence.

For instance, consider the sentence ``A coronary angioplasty may not be technically possible'',
which was translated by one of the systems we experimented with as
``Eine koronare Angioplastie kann nicht technisch m{\"o}glich'', i.e., the main verb ``sein'' (``be'') is omitted.
While this may be interpreted is a minor error, HMEANT will assign it a very low score, as it failed to
translate the main verb.

We understand that this is a design feature of HMEANT:
if the translation per se cannot be annotated with verbal argument structure
(for whatever reason, including incomprehensibility), it cannot convey the meaning.

HMEANT thus makes a stricter check of whether the translation can be understood
than we do. HUME may be artificially boosting the perceived understandability of
the sentence by providing the source.

\subsection{Importance of Alignment}

In HMEANT, the alignment between the (source and candidate) structures is a key
part of the manual annotation. If the alignment cannot be created, the candidate
translation is heavily penalized in score.
Previous experiments with HMEANT
\parcite{bojar:wu:ssst:2012,chuchunkov-tarelkin-galinskaya:2014:SSST-8} have
suggested that modifications to the two structures are desirable and appropriate
at the alignment stage, to avoid unduly penalization due to spurious diverges in
the structures.
The same issue was observed by HMEANT authors themselves \parcite{XXXcite}
\XXX{cite this: http://repository.ust.hk/ir/Record/1783.1-66107}: the
inter-annotator agreement on SRL dropped from 90\% to 61\% 
when the two aligned structures were from two different annotators.

HUME uses only automatic (word-level) alignment, and it's only purpose is to
make the annotation process easier. The alignment is indicative only and the
user is expected to mentally correct the alignment as needed.

\subsection{Monolingual vs. Bilingual Evaluation}
HUME diverges from HMEANT (and also from the shallow automatic measures
like BLEU or
METEOR) in not requiring a reference.
Instead, it compares the source directly with the output
translation.

This requires us to employ bilingual annotators, but has the benefit of avoiding
the reference translation. It is known that the reference translations are not
always literal enough and the MT output semantics can be composed differently
than the semantics of the reference. While this is in principle not a problem
for HUME (the whole sentence can be labelled as ``Green''), it prevents learning
any fine-grained information about the MT output.

Perhaps even more importantly,
the reference translations were often not created by translating the source
sentences. In some cases, the manual translation was reversed, or both the
``source'' and ``reference'' are actually independent translations from a third
language. The ``reference'' can thus easily contain more information than the
``source''.

@@

\subsection{XXX to be removed}

In the *MEANT papers they mainly test by either
A) correlating the metric to ranking judgements; or
B) using automated versions of the metric for tuning MT systems

@@

%Here is an additional argument to support the need for target-only intelligibility:
%http://www.aclweb.org/anthology/W14-4005
%see Table  3 and the text in Section 5.2.
%The more frames can people annotate in the hypothesis, the better the hypothesis overall.
